This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
#source("class_LocationData.R")
source("class_ModuleOutput.R")
source("harvest-processing.R")
source("prescribed-burn-functions.R")
source("decay-functions.R")
source('wildfire-functions.R')
source('power-plant-functions.R')
source("misc-functions.R")
```

Load needed library functions
```{r}
load.libraries(c("data.table","raster","rgdal","rgeos","dplyr","beepr")) # beepr is for testing

```

To make multiple runs with different options, easier, we're putting all user options and filepaths in an external csv file,
which we read in here.
```{r}
user_input_filepath <- '/Volumes/744GB-Storage/Dropbox/serc/carbcat/cbrec_inputs.csv'
user_inputs <- data.table(read.csv(user_input_filepath, stringsAsFactors = FALSE))
```

Load up emissions factor/rate data from csv files.
```{r}
equipment_emissions <- data.table(read.csv(user_inputs[variable=='equipment_emissions_filepath',value]))

```

Load up the location-specific information gleaned from GIS data. 
To load up the location-specific date, first we load the FCID_code ratser layer.This has over a billion data points, and may
crash RStudio. In many cases, we will crop the dataset down to a shapefile supplied by the user (or, more accurately, mask the dataset).
If the dataset is full, most of those points are empty. In either case, once loaded, convert the RasterLayer to a data frame, and extract
the subset of points that correspond to actual data. 

Once we have the smaller data set, convert to a data table and combine with the residue and decay tables.

ANDY: LOOK HERE
Our model runs cases individually, rather than paired scenarios, because of memory constraints of running two data pairs in a single run. BUT scenarios are going to cover the same geographic study area, 
and the most runtime-heavy code segment is the raster cropping and masking. So, if the first time we run a case, we run the raster process, save the resultant study_area_FCID, and THEN apply scenario_matrix
variables, we make this whiole thing run much quicker. This will require clear design for input/output file structure.

For agricultural data:
(TBA)
```{r}
if(user_inputs[variable=='ag_or_forest',value]=='forest') {
  study_area_raster <- raster(user_inputs[variable=='fcid_code_filepath',value])
  slope_raster <- raster(user_inputs[variable=='slope_filepath',value])
  names(slope_raster) <- "cell_slope"

  # If the user inputs specify a study area mask file, load the shapefile, crop the original raster to the shapefile extents, and mask the raster to the shape file.
  if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
    study_area_mask <- readOGR(user_inputs[variable=='study_area_mask_file',value])
    study_area_raster <- crop(study_area_raster,extent(study_area_mask))
    study_area_raster <- mask(study_area_raster,study_area_mask)
    slope_raster <- crop(slope_raster,extent(study_area_mask))
    slope_raster <- mask(slope_raster,study_area_mask)
  }
  
  # convert raster objects to data frames. This may crash things.
    ##########################################################################################
  ##########################################################################################
  # Look into if we can combine the subset line below into the as.data.frame line here. Also, 
  # look if we can stack FCID and slope rasters to see if we can load them at the same time.
  ##########################################################################################
    ##########################################################################################
  study_area_df <- as.data.frame(study_area_raster,xy=TRUE)
  
  names(study_area_df) <- c('x','y','FCID_code')
  
  # The full raster dataset is a square, so it will include non-forested areas within California, a chunk of the Pacifc Ocean,
  # and a fair bit of Nevada. These locations will have an FCID value of NA; trim it out using subset()
  study_area_df <- subset(study_area_df,!is.na(FCID_code))
  
  # Repeat with slope
  slope_df <- as.data.frame(slope_raster,xy=TRUE)
  slope_df <- subset(slope_df,!is.na(cell_slope))
  
  # Convert to a data table, and delete the data frame
  study_area_FCID <- data.table(study_area_df)
  study_area_df <- NULL
  setkey(study_area_FCID,x,y)
  
  # Repeat with slope
  slope_dt <- data.table(slope_df)
  slope_df <- NULL
  setkey(slope_dt,x,y)

  # Combine the slope with the FCID data tables - THIS MAY NOT BE NECESSARY IF WE CAN LOAD AS STACKS.
  study_area_FCID <- slope_dt[study_area_FCID]

  # Delete the slope data table to save on memory
  slope_dt <- NULL
  
  # Read in the residue load values from a csv file. These values are indexed by FCID_code, so that is how we will join the 2 tables
  fcid_table <- data.table(read.csv(user_inputs[variable=='residue_treatment_filepath',value]))
  setkey(fcid_table,FCID2018)
  setkey(study_area_FCID,FCID_code)
  study_area_FCID <- study_area_FCID[fcid_table[Treatment==user_inputs[variable=='treatment_type',value]]]
  setkey(study_area_FCID,x,y)
  
  # There will be some overlap for FCID values that don't appear in the data set. They will have non-existant x & y values. Trim them.
  study_area_FCID <- study_area_FCID[!is.na(x)]
  
  # Round the x and y values to the first decimal, otherwise rounding errors are going to muck with joins with the decay rates.
  study_area_FCID[,':='(x=round(x,digits=1),y=round(y,digits=1))]
  
  # Eliminate the treatment columns, we do not need it. The FCID code is still needed for power plant efficiency.
  study_area_FCID[,Treatment:=NULL]
  
  # Time to add information about the biomass properties, specifically heating value and carbon fraction. 
  biomass_properties <- data.table(read.csv(user_inputs[variable=='biomass_properties_filepath',value]))
  setkey(biomass_properties,FCID_code)
  setkey(study_area_FCID,FCID_code)
  study_area_FCID <- biomass_properties[study_area_FCID]
  
  # Re-key
  setkey(study_area_FCID,x,y)
  
  ################################################################################################################
  # We may be able to eliminate the Carbon_frac column. Check the script when complete, it may save some RAM/time.
  ################################################################################################################
}

if(user_inputs[variable=='ag_or_forest',value]=='agricultural') {
  print('This code has yet to be written')
}

beep(5)
```

Load the decay rate rasters
```{r}
# There are currently 3 decay rasters: one for CWD, FWD, and foliage. From our notes, there should be six rates (for piled and scattered), not just 3.
# Figure out if this is an issue.
CWD_decay_raster <- raster(user_inputs[variable=='CWD_decay_filepath',value])
FWD_decay_raster <- raster(user_inputs[variable=='FWD_decay_filepath',value])
foliage_decay_raster <- raster(user_inputs[variable=='foliage_decay_filepath',value])

# If the user inputs specify a study area mask file, we will have a shapefile loaded from earlier. Use the same shape file to crop and mask our rasters.
if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
  # CWD raster
  CWD_decay_raster <- crop(CWD_decay_raster,extent(study_area_mask))
  CWD_decay_raster <- mask(CWD_decay_raster,study_area_mask)
  
  # FWD raster  
  FWD_decay_raster <- crop(FWD_decay_raster,extent(study_area_mask))
  FWD_decay_raster <- mask(FWD_decay_raster,study_area_mask)
  
  # foliage raster
  foliage_decay_raster <- crop(foliage_decay_raster,extent(study_area_mask))
  foliage_decay_raster <- mask(foliage_decay_raster,study_area_mask)
}

# Now that the decay rasters are loaded and masked, convert them to data frames and then data tables
CWD_decay_df <- as.data.frame(CWD_decay_raster,xy=TRUE)
CWD_decay_rates <- data.table(CWD_decay_df)
CWD_decay_df <- NULL
setkey(CWD_decay_rates,x,y)
CWD_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

FWD_decay_df <- as.data.frame(FWD_decay_raster,xy=TRUE)
FWD_decay_rates <- data.table(FWD_decay_df)
FWD_decay_df <- NULL
setkey(FWD_decay_rates,x,y)
FWD_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

foliage_decay_df <- as.data.frame(foliage_decay_raster,xy=TRUE)
foliage_decay_rates <- data.table(foliage_decay_df)
foliage_decay_df <- NULL
setkey(foliage_decay_rates,x,y)
foliage_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

# Join decay data tables with the study area FCID, and then clear the data tables
setkey(study_area_FCID,x,y)
setkey(CWD_decay_rates,x,y)
setkey(FWD_decay_rates,x,y)
setkey(foliage_decay_rates,x,y)

study_area_FCID <- CWD_decay_rates[FWD_decay_rates[foliage_decay_rates[study_area_FCID]]]

# There may be a couple more NA points, with no reource available and no decay rate assigned. Clear it out.
study_area_FCID <- study_area_FCID[!is.na(CWD_cm)&!is.na(FWD_cm)&!is.na(Foliage_cm),]

CWD_decay_rates <- NULL
FWD_decay_rates <- NULL
foliage_decay_rates <- NULL

beep(4)
```

Load some premade data for development and debugging.
```{r}
# load('/Volumes/744GB-Storage/CBREC R data/study_area_FCID.Rdata')
# 
# # We'll need the shape file 
# if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
#     study_area_mask <- readOGR(user_inputs[variable=='study_area_mask_file',value])
# }
# 
# beep(4)
```

We now have a spatially-indexed data table with residue loading information, decay rates, and cell slope values These values should be the same for every study area.
Now we figure out what the technically recoverable residue is.

```{r}
# The technically available residues will be based on silvicultural treatment, harvest system/type (currently the harvest_system column),
# burn type, biomass collection, and pulp market. Within a scenario, treatment, burn type, biomass collection, and pulp market are decided 
# across the entire study area. Harvest system will vary based on slope. Rather than create an ID for study_area_FCID and merging with the complete scenario martix,
# create a smaller scenario matrix filtered through the user inputs, and merge with study_area_FCID based upon harvest_system.
complete_scenario_matrix <- data.table(read.csv(user_inputs[variable=='scenario_matrix_file',value]))

# Trim to the treatment, burn type, biomass collection, and pulp market
scenario_matrix <- copy(complete_scenario_matrix[Fraction_Piled_Residues==user_inputs[variable=='fraction_piled_residues',value] &
                                                 Silvicultural.Treatment==user_inputs[variable=='treatment_type',value] & 
                                                 Burn.Type==user_inputs[variable=='burn_type',value] & 
                                                 Biomass.Collection==user_inputs[variable=='biomass_collection',value] & 
                                                 Pulp.Market==user_inputs[variable=='has_pulp_market',value],])

########################################
# Combine stem and bark residues.
########################################

# Merge senario matrix with study_area_FCID; this will be based on cell slope (>40%, <40%, or remove from study)
scenario_matrix[,':='(ID=NULL, Fraction_Piled_Residues=NULL, Fraction_Scattered_Residues=NULL, Silvicultural.Treatment=NULL, Burn.Type=NULL, Biomass.Collection=NULL, Pulp.Market=NULL)]
setkey(scenario_matrix,Slope)

###########################################################
###########################################################
# We may be able to speed this up by converting to factors
###########################################################
###########################################################
setkey(study_area_FCID,cell_slope)
study_area_FCID[,merge_column := "GT40"]
study_area_FCID[cell_slope<40,merge_column := "LT40"]

# Delete entries after the slope cutoff point
study_area_FCID <- study_area_FCID[cell_slope<as.numeric(user_inputs[variable=='residue_slope_cutoff',value])]

# Merge study_area_FCID with the scenario matrix
setkey(study_area_FCID,merge_column)
study_area_FCID <- scenario_matrix[study_area_FCID]

# Combine the technically available fractions with the gross resource base.
study_area_FCID[,':='(Recovered_Stem9Plus_tonsAcre = Recovered_Stem9Plus * Stem9Plus_tonsAcre,
                   Recovered_Stem6to9_tonsAcre = Recovered_Stem6to9 * Stem6to9_tonsAcre,
                   Recovered_Stem4to6_tonsAcre = Recovered_Stem4to6 * Stem4to6_tonsAcre,
                   Recovered_Bark9Plus_tonsAcre = Recovered_Bark9Plus * Bark9Plus_tonsAcre,
                   Recovered_Bark6to9_tonsAcre = Recovered_Bark6to9 * Bark6to9_tonsAcre,
                   Recovered_Bark4to6_tonsAcre = Recovered_Bark4to6 * Bark4to6_tonsAcre,
                   Recovered_Branch_tonsAcre = Recovered_Branch * Branch_tonsAcre,
                   Recovered_Foliage_tonsAcre = Recovered_Foliage * Foliage_tonsAcre,
                   Merchantable_Stem9Plus_tonsAcre = Merchantable_Stem9Plus * Stem9Plus_tonsAcre,
                   Merchantable_Stem6to9_tonsAcre = Merchantable_Stem6to9 * Stem6to9_tonsAcre,
                   Merchantable_Stem4to6_tonsAcre = Merchantable_Stem4to6 * Stem4to6_tonsAcre,
                   Merchantable_Bark9Plus_tonsAcre = Merchantable_Bark9Plus * Bark9Plus_tonsAcre,
                   Merchantable_Bark6to9_tonsAcre = Merchantable_Bark6to9 * Bark6to9_tonsAcre,
                   Merchantable_Bark4to6_tonsAcre = Merchantable_Bark4to6 * Bark4to6_tonsAcre,
                   Merchantable_Branch_tonsAcre = Merchantable_Branch * Branch_tonsAcre,
                   Merchantable_Foliage_tonsAcre = Merchantable_Foliage * Foliage_tonsAcre,
                   Piled_Stem9Plus_tonsAcre = Piled_Stem9Plus * Stem9Plus_tonsAcre,
                   Piled_Stem6to9_tonsAcre = Piled_Stem6to9 * Stem6to9_tonsAcre,
                   Piled_Stem4to6_tonsAcre = Piled_Stem4to6 * Stem4to6_tonsAcre,
                   Piled_Bark9Plus_tonsAcre = Piled_Bark9Plus * Bark9Plus_tonsAcre,
                   Piled_Bark6to9_tonsAcre = Piled_Bark6to9 * Bark6to9_tonsAcre,
                   Piled_Bark4to6_tonsAcre = Piled_Bark4to6 * Bark4to6_tonsAcre,
                   Piled_Branch_tonsAcre = Piled_Branch * Branch_tonsAcre,
                   Piled_Foliage_tonsAcre = Piled_Foliage * Foliage_tonsAcre,
                   Scattered_Stem9Plus_tonsAcre = Scattered_Stem9Plus * Stem9Plus_tonsAcre,
                   Scattered_Stem6to9_tonsAcre = Scattered_Stem6to9 * Stem6to9_tonsAcre,
                   Scattered_Stem4to6_tonsAcre = Scattered_Stem4to6 * Stem4to6_tonsAcre,
                   Scattered_Bark9Plus_tonsAcre = Scattered_Bark9Plus * Bark9Plus_tonsAcre,
                   Scattered_Bark6to9_tonsAcre = Scattered_Bark6to9 * Bark6to9_tonsAcre,
                   Scattered_Bark4to6_tonsAcre = Scattered_Bark4to6 * Bark4to6_tonsAcre,
                   Scattered_Branch_tonsAcre = Scattered_Branch * Branch_tonsAcre,
                   Scattered_Foliage_tonsAcre = Scattered_Foliage * Foliage_tonsAcre
)]

# Trim out the columns we no longer need. ###### REMOVING SLOPE FOR NOW ######
study_area_FCID[,':='(Slope=NULL, Recovered_Stem9Plus = NULL, Stem9Plus_tonsAcre = NULL, Recovered_Stem6to9 = NULL, Stem6to9_tonsAcre = NULL, Recovered_Stem4to6 = NULL,
                   Stem4to6_tonsAcre = NULL, Recovered_Bark9Plus = NULL, Bark9Plus_tonsAcre = NULL, Recovered_Bark6to9 = NULL, Bark6to9_tonsAcre = NULL,
                   Recovered_Bark4to6 = NULL, Bark4to6_tonsAcre = NULL, Recovered_Branch = NULL, Branch_tonsAcre = NULL, Recovered_Foliage = NULL,
                   Foliage_tonsAcre = NULL, Merchantable_Stem9Plus = NULL, Merchantable_Stem6to9 = NULL, Merchantable_Stem4to6 = NULL,  Merchantable_Bark9Plus = NULL,
                   Merchantable_Bark6to9 = NULL, Merchantable_Bark4to6 = NULL, Merchantable_Branch = NULL, Merchantable_Foliage = NULL, Piled_Stem9Plus = NULL, 
                   Piled_Stem6to9 = NULL, Piled_Stem4to6 = NULL, Piled_Bark9Plus = NULL, Piled_Bark6to9 = NULL, Piled_Bark4to6 = NULL, Piled_Branch = NULL, Piled_Foliage = NULL,
                   Scattered_Stem9Plus = NULL, Scattered_Stem6to9 = NULL, Scattered_Stem4to6 = NULL, Scattered_Bark9Plus = NULL, Scattered_Bark6to9 = NULL,
                   Scattered_Bark4to6 = NULL, Scattered_Branch = NULL, Scattered_Foliage = NULL
)]

```

Add wildfire data and emissions factors. These are stored in .rds files by tile; there are over 13,000 tiles. We need to load the tile data that overlaps with
our study area, then the data needs to be cropped to match our study area exactly.

*NOTE* The fill wildfire data has not been processed yet, so to test out this operation, I am probably going to need to make some dummy data.

```{r}
# Load up the full tile shape file
full_tile_set <- readOGR(user_inputs[variable=="tile_shape_file",value])
study_area_tiles <- raster::intersect(study_area_mask,full_tile_set)

# To get the tile IDs, convert study_area_tiles into a data frame and extract the ID column
tile_list <- as.data.frame(study_area_tiles)$ID

wildfire_data <- data.table()

# Cycle through tile_list, load the .rds files, and combine into a single data table.
for (tile in tile_list) {
  new_tile <- readRDS(paste(user_inputs[variable=="wildfire_data_directory",value],tile,".rds",sep=""))
  tile_data <- data.table(as.data.frame(new_tile,xy=TRUE))
  setkey(tile_data,x,y)
  wildfire_data <- rbind(wildfire_data,tile_data)
  tile_data <- NULL
}

# Round the x and y values to the first decimal, otherwise rounding errors are going to muck with joins.
wildfire_data[,':='(x=round(x,digits=1),y=round(y,digits=1))]
setkey(wildfire_data,x,y)

##############################################################################################################
##############################################################################################################
# BECAUSE WE ARE USING DUMMY DATA, WE NEED TO RENAME AND CREATE SOME MORE REALISTIC DUMMY DATA.
##############################################################################################################
##############################################################################################################
setnames(wildfire_data,"UW_FCID_no_wild","MassExposedToWildfire")
wildfire_data[,':='(MassExposedToWildfire = MassExposedToWildfire / 1e10,
                    CWD_CombustionFrac = runif(nrow(wildfire_data)),
                    FWD_CombustionFrac = runif(nrow(wildfire_data)),
                    Foliage_CombustionFrac = runif(nrow(wildfire_data))
                    )]

wildfire_data[,':='(CWD_CharFrac = (2/3) * (1 - CWD_CombustionFrac),
                    FWD_CharFrac = (2/3) * (1 - FWD_CombustionFrac),
                    Foliage_CharFrac = (2/3) * (1 - Foliage_CombustionFrac)
                    )]

wildfire_data[,':='(CWD_UnburnedFrac = 1 - CWD_CombustionFrac - CWD_CharFrac,
                    FWD_UnburnedFrac = 1 - FWD_CombustionFrac - FWD_CharFrac,
                    Foliage_UnburnedFrac = 1 - Foliage_CombustionFrac - Foliage_CharFrac
                    )]

# Merge the wildfire data with study_area_FCID
study_area_FCID <- wildfire_data[study_area_FCID]
```

Column preparation for Burn/Decay/Wildfire Emissions
```{r}
# Step 1: combine all mass categories into CWD, FWD, and foliage. There will also be a duff column, though this will start empty. 
# There will be several categories with different decay rates - recovered, scattered (including merchantable breakage), field piled, and landing piled
study_area_FCID[,':='(Recovered_CWD_tonsAcre = Recovered_Stem9Plus_tonsAcre + Recovered_Stem6to9_tonsAcre + Recovered_Stem4to6_tonsAcre + Recovered_Bark9Plus_tonsAcre + Recovered_Bark6to9_tonsAcre + Recovered_Bark4to6_tonsAcre,
                      Scattered_CWD_tonsAcre = Merchantable_Stem9Plus_tonsAcre + Merchantable_Stem6to9_tonsAcre + Merchantable_Stem4to6_tonsAcre + Merchantable_Bark9Plus_tonsAcre + Merchantable_Bark6to9_tonsAcre + Merchantable_Bark4to6_tonsAcre + Scattered_Stem9Plus_tonsAcre + Scattered_Stem6to9_tonsAcre + Scattered_Stem4to6_tonsAcre + Scattered_Bark9Plus_tonsAcre + Scattered_Bark6to9_tonsAcre + Scattered_Bark4to6_tonsAcre,
                      Piled_CWD_tonsAcre = Piled_Stem9Plus_tonsAcre + Piled_Stem6to9_tonsAcre + Piled_Stem4to6_tonsAcre + Piled_Bark9Plus_tonsAcre + Piled_Bark6to9_tonsAcre + Piled_Bark4to6_tonsAcre
)]

# Clear out old columns, as well as merchantable branch/foliage (which should've been empty anyway)
study_area_FCID[,':='(Recovered_Stem9Plus_tonsAcre = NULL, Recovered_Stem6to9_tonsAcre = NULL, Recovered_Stem4to6_tonsAcre = NULL, Recovered_Bark9Plus_tonsAcre = NULL, Recovered_Bark6to9_tonsAcre = NULL, 
                      Recovered_Bark4to6_tonsAcre = NULL, Merchantable_Stem9Plus_tonsAcre = NULL, Merchantable_Stem6to9_tonsAcre = NULL, Merchantable_Stem4to6_tonsAcre = NULL, Merchantable_Bark9Plus_tonsAcre = NULL,
                      Merchantable_Bark6to9_tonsAcre = NULL, Merchantable_Bark4to6_tonsAcre = NULL, Merchantable_Branch_tonsAcre=NULL, Merchantable_Foliage_tonsAcre = NULL, Scattered_Stem9Plus_tonsAcre = NULL,
                      Scattered_Stem6to9_tonsAcre = NULL, Scattered_Stem4to6_tonsAcre = NULL, Scattered_Bark9Plus_tonsAcre = NULL, Scattered_Bark6to9_tonsAcre = NULL, Scattered_Bark4to6_tonsAcre = NULL,
                      Piled_Stem9Plus_tonsAcre = NULL, Piled_Stem6to9_tonsAcre = NULL, Piled_Stem4to6_tonsAcre = NULL, Piled_Bark9Plus_tonsAcre = NULL, Piled_Bark6to9_tonsAcre = NULL, Piled_Bark4to6_tonsAcre = NULL
)]

# FWD consists of branches, and foliage is obviously foliage. Just rename the columns.
setnames(study_area_FCID,
         c("Recovered_Branch_tonsAcre","Piled_Branch_tonsAcre","Scattered_Branch_tonsAcre"),
         c("Recovered_FWD_tonsAcre","Piled_FWD_tonsAcre","Scattered_FWD_tonsAcre"))

# Copy the residue columns for Piled and Scattered residues. These will be the initial mass residues in Year 1. We will also need some blank columns to track material exposed to fire but left unburned.
study_area_FCID[,':='(Recovered_CWD_tonsAcre_INITIAL = Recovered_CWD_tonsAcre,
                      Recovered_FWD_tonsAcre_INITIAL = Recovered_FWD_tonsAcre,
                      Recovered_Foliage_tonsAcre_INITIAL = Recovered_Foliage_tonsAcre,
                      Piled_CWD_tonsAcre_INITIAL = Piled_CWD_tonsAcre,
                      Piled_FWD_tonsAcre_INITIAL = Piled_FWD_tonsAcre,
                      Piled_Foliage_tonsAcre_INITIAL = Piled_Foliage_tonsAcre,
                      Scattered_CWD_tonsAcre_INITIAL = Scattered_CWD_tonsAcre,
                      Scattered_FWD_tonsAcre_INITIAL = Scattered_FWD_tonsAcre,
                      Scattered_Foliage_tonsAcre_INITIAL = Scattered_Foliage_tonsAcre
                      )]

# Make columns for duff, mass previously exposed to fire but unburnt, and year.i columns. If space becomes an issue, we can create/delete year.i column in the decay function, but I;m guessing that will hit our speed.
study_area_FCID[,':='(Duff_tonsAcre=0, decay_CWD_mass_year_i=0, decay_FWD_mass_year_i=0, decay_Foliage_mass_year_i=0,
                      fire_exposed_CWD_mass_year_i=0, fire_exposed_FWD_mass_year_i=0, fire_exposed_Foliage_mass_year_i=0, fire_exposed_Duff_mass_year_i=0,
                      prev_fired_CWD_tonsAcre=0, prev_fired_FWD_tonsAcre=0, prev_fired_Foliage_tonsAcre=0, prev_fired_Duff_tonsAcre=0)]

century_emissions_profile <- data.table(CO2_tonnes=rep(0,100), CO_tonnes=rep(0,100), N2O_tonnes=rep(0,100), CH4_tonnes=rep(0,100), NOx_tonnes=rep(0,100), PMUnder10um_tonnes=rep(0,100), PMUnder2.5um_tonnes=rep(0,100), SOx_tonnes=rep(0,100), VOC_tonnes=rep(0,100), char_tonnes=rep(0,100))

# Cycle through 100 years of emissions. Each year, we need to:
# 1) Calculate the mass lost in year i
# 2) Use the mass lost to atmosphere/duff ratios to calculate the mass lost to duff and atmosphere
# 3) Update the dynamic residue mass
# 4) Apply decay to the duff column, add emissions to emissions columns, and update duff mass.

# Output should be a 100 row-X xolumn data table of combined emissions for study area by emissions type (i.e. decay, wildfire, other use....). See output template for more info.

```

If our case involves biomass collection, transportation and equipment becomes an issue. This will involve more raster work, which will take a little time. So, let's skip it if biomass collection ain't happening.
```{r}
if(user_inputs[variable=="biomass_collection",value]!="No") {
  
  #######################################################################################################################################
  # Determine specific travel distances - cell to road, then road to plant.
  #######################################################################################################################################
  
  # Load the cell to road raster. Be sure to trim to the study area, or we may hit memory problems.
  cell_to_road_raster <- raster(user_inputs[variable=="cell_to_road_dist_filepath",value])
  cell_to_road_raster <- crop(cell_to_road_raster,extent(study_area_mask))
  cell_to_road_raster <- mask(cell_to_road_raster,study_area_mask)
  cell_to_road <- as.data.frame(cell_to_road_raster,xy=T)
  cell_to_road <- data.table(cell_to_road)

  # Rename the value column, bearing in mind that the distance raster is in meters.
  setnames(cell_to_road,c('x','y','CellToRoadDist_meters'))

  # Convert the meters to miles; eliminate meters
  cell_to_road[,CellToRoadDist_miles := CellToRoadDist_meters * 0.000621371]
  cell_to_road[,CellToRoadDist_meters := NULL]

  # Combine with studay_area_FCID. This first requires rounding coordinates to the nearest tenth.
  cell_to_road[,':='(x=round(x,digits=1),y=round(y,digits=1))]
  setkey(cell_to_road,x,y)
  study_area_FCID <- cell_to_road[study_area_FCID]

  # Repeat for the road to plant raster. Trim to the study area, or we may hit memory problems.
  road_to_plant_raster <- raster(user_inputs[variable=="road_to_plant_dist_filepath",value])
  road_to_plant_raster <- crop(road_to_plant_raster,extent(study_area_mask))
  road_to_plant_raster <- mask(road_to_plant_raster,study_area_mask)
  
  road_to_plant <- as.data.frame(road_to_plant_raster,xy=T)
  
  beep(5)
  
  # The transportation rasters are compressed, so as.data.frame will get all coordinates, but lose much of the data. This line gets it back.
  road_to_plant$RoadToPlant_miles <- road_to_plant_raster[] %>% as.double()
  
  # Trim uneeded columns, convert to data frame.
  road_to_plant <- road_to_plant %>% select(x,y,RoadToPlant_miles)
  road_to_plant <- data.table(road_to_plant)
  
  # Combine with study_area_FCID. This first requires rounding coordinates to the nearest tenth.
  road_to_plant[,':='(x=round(x,digits=1),y=round(y,digits=1))]
  setkey(road_to_plant,x,y)
  
  # Add a column to indicate the specific plant location. This is set in the user variables.
  road_to_plant[,plant_location:=user_inputs[variable=="power_plant_location",value]]
  study_area_FCID <- road_to_plant[study_area_FCID]
  
  # Combine cell-to-road and road-to-plant miles, and then trim the old columns
  study_area_FCID[,TotalRoad_miles := RoadToPlant_miles + CellToRoadDist_miles]
  study_area_FCID[,':='(RoadToPlant_miles = NULL, CellToRoadDist_miles = NULL)]
  
  # Now to determine equipment. This will vary depending on whther the harvest is high or low volume; this will be determined through average cell residue density

  #######################################################################################################################################
  #######################################################################################################################################
  # We've got a few cells missing wildfire exposure. For now, delete them, this may be a problem for the full study.
  #######################################################################################################################################
  #######################################################################################################################################
  study_area_FCID <- study_area_FCID[!is.na(MassExposedToWildfire),]
  
  #######################################################################################################################################
  # Calculate harvest/processing emissions, and adjust mass totals.
  #######################################################################################################################################
  high_volume_cell_threshold_density <- 13 # BDT/scre; remember that tons/acre is the unit for all of our residues.
  processing_mass_loss <- 0.05 # % of mass lost during processing; assumed constant for all equipment. Unprocessed mass is left to decay or be exposed to wildfire.
  # WE STILL WANT TO DO THE BELOW NOTE?
  # Build something similar to processing mass loss for transportation losses, value currently at 0%.
  
  harvest_processing_output <- harvest_processing_fun(study_area_FCID, high_volume_cell_threshold_density,processing_mass_loss)
  harvest_processing_emissions <- harvest_processing_output[[1]]
  study_area_FCID <- harvest_processing_output[[2]]
  
  #######################################################################################################################################
  # Calculate power plant emissions.
  #######################################################################################################################################
  power_emission_factors <- data.table(read.csv(user_inputs[variable=='power_plant_emissions_filepath',value]))
  
  if(user_inputs[variable=='power_plant_location',value]=='Nearest') { # Multiple potential power plant locations
    power_plant_output <- power_plant_fun(study_area_FCID, power_emission_factors, unique(study_area_FCID[,plant_location]))
    power_plant_emissions <- power_plant_output[[1]]
    power_plant_production <- power_plant_output[[2]]
  } else { # Single power plant location
    power_plant_output <- power_plant_fun(study_area_FCID, power_emission_factors, user_inputs[variable=='power_plant_location',value])
    power_plant_emissions <- power_plant_output[[1]]
    power_plant_production <- power_plant_output[[2]]
  }
  
  # Add the harvesting and power plant emissions to year 1 of the century emissions profile. Emissions are given in kg, we need them in tonnes
  century_emissions_profile[1,':='(CO2_tonnes = (harvest_processing_emissions[,CO2_kg] + power_plant_emissions[,CO2_kg])/1000,
                                   CO_tonnes = (harvest_processing_emissions[,CO_kg] + power_plant_emissions[,CO_kg])/1000,
                                   N2O_tonnes = (harvest_processing_emissions[,N2O_kg] + power_plant_emissions[,N2O_kg])/1000,
                                   CH4_tonnes = (harvest_processing_emissions[,CH4_kg] + power_plant_emissions[,CH4_kg])/1000,
                                   NOx_tonnes = (harvest_processing_emissions[,NOx_kg] + power_plant_emissions[,NOx_kg])/1000,
                                   PMUnder10um_tonnes = (harvest_processing_emissions[,PMUnder10um_kg] + power_plant_emissions[,PMUnder10um_kg])/1000,
                                   PMUnder2.5um_tonnes = (harvest_processing_emissions[,PMUnder2.5um_kg] + power_plant_emissions[,PMUnder2.5um_kg])/1000,
                                   SOx_tonnes = (harvest_processing_emissions[,SOx_kg] + power_plant_emissions[,SOx_kg])/1000,
                                   VOC_tonnes = (harvest_processing_emissions[,VOC_kg] + power_plant_emissions[,VOC_kg])/1000,
                                   char_tonnes = (harvest_processing_emissions[,char_kg] + power_plant_emissions[,char_kg])/1000)]
}

```


We need to remove the residue segemnt for loop. We don't need it, and it slows processing down considerably. Modular code seems to be just as fast, and makes comprehension easier.
Keep the modular code, and remove the residue segment for loop; once we have completed our formula verification, remove the emissions_year_i and char_year_i rows (there are 200 total).
See code examples below for clarification.

Modular code. "2019-03-22 12:37:02 PDT" to "2019-03-22 14:08:06 PDT"
```{r}
Sys.time()
for (year.i in 1:100) {
  print(year.i)
  
  # A few things will happen only in year 1 (if at all): residues collection (and processing, transportations, and power plant use), and prescribed burning.
  # Harvesting, processing, transportation, and power plant emissions will have been addressed already, because there is an easy variable (biomass_collection)
  # Calculate emissions and mass loss from these activities before decay/wildfire. Note: they will affect different residue segments, so it does not matter 
  # if if prescribed burning or collection comes first.
  if(year.i==1) {
    
    # Make sure that the residue segment matches correctly with the prescribed burn method
    if(user_inputs[variable=='burn_type',value] == "Broadcast Burn") {
      prescribed_burn_output <- prescribed_burn_fun(study_area_FCID, "Scattered", user_inputs[variable=='burn_type',value])
      prescribed_burn_emissions <- prescribed_burn_output[[1]]
      study_area_FCID <- prescribed_burn_output[[2]]
    }
    if(user_inputs[variable=='burn_type',value] == "Pile Burn") {
      prescribed_burn_output <- prescribed_burn_fun(study_area_FCID, "Piled", user_inputs[variable=='burn_type',value])
      prescribed_burn_emissions <- prescribed_burn_output[[1]]
      study_area_FCID <- prescribed_burn_output[[2]]
    }
    if(user_inputs[variable=='burn_type',value] == "Pile and Broadcast Burn") {
      prescribed_burn_output <- prescribed_burn_fun(study_area_FCID, "Piled", user_inputs[variable=='burn_type',value])
      prescribed_burn_emissions <- prescribed_burn_output[[1]]
      study_area_FCID <- prescribed_burn_output[[2]]
      
      prescribed_burn_output <- prescribed_burn_fun(study_area_FCID, "Scattered", user_inputs[variable=='burn_type',value])
      prescribed_burn_emissions <- prescribed_burn_emissions + prescribed_burn_output[[1]]
      study_area_FCID <- prescribed_burn_output[[2]]
    }
    
    # Add to the century emissions profile
    century_emissions_profile[year.i,':='(CO2_tonnes = CO2_tonnes + prescribed_burn_emissions[,CO2_tonnes],
                                          CO_tonnes = CO_tonnes + prescribed_burn_emissions[,CO_tonnes],
                                          N2O_tonnes = N2O_tonnes + prescribed_burn_emissions[,N2O_tonnes],
                                          CH4_tonnes = CH4_tonnes + prescribed_burn_emissions[,CH4_tonnes],
                                          NOx_tonnes = NOx_tonnes + prescribed_burn_emissions[,NOx_tonnes],
                                          PMUnder10um_tonnes = PMUnder10um_tonnes + prescribed_burn_emissions[,PMUnder10um_tonnes],
                                          PMUnder2.5um_tonnes = PMUnder2.5um_tonnes + prescribed_burn_emissions[,PMUnder2.5um_tonnes],
                                          SOx_tonnes = SOx_tonnes + prescribed_burn_emissions[,SOx_tonnes],
                                          VOC_tonnes = VOC_tonnes + prescribed_burn_emissions[,VOC_tonnes],
                                          char_tonnes = char_tonnes + prescribed_burn_emissions[,char_tonnes])]
  }
  
  # Calculate the total decayed mass. "Previously Fired" must be a category; addressing previously fired material decay in each segment will run that decay 3 times over.
  decay_output <- decay_fun(study_area_FCID,residue.segment = "Scattered",year.i)
  decay_emissions <- decay_output[[1]]
  study_area_FCID <- decay_output[[2]]
  
  decay_output <- decay_fun(study_area_FCID,residue.segment = "Piled",year.i)
  decay_emissions <- decay_emissions + decay_output[[1]]
  study_area_FCID <- decay_output[[2]]
  
  decay_output <- decay_fun(study_area_FCID,residue.segment = "Recovered",year.i)
  decay_emissions <- decay_emissions + decay_output[[1]]
  study_area_FCID <- decay_output[[2]]
  
  decay_output <- decay_fun(study_area_FCID,residue.segment = "prev_fired",year.i)
  decay_emissions <- decay_emissions + decay_output[[1]]
  study_area_FCID <- decay_output[[2]]
  
  # Repeat for duff. Because we only run duff decay once, we can address both previously fired and non-fired duff.
  decay_output <- duff_decay_fun(study_area_FCID,year.i)
  decay_emissions <- decay_emissions + decay_output[[1]]
  study_area_FCID <- decay_output[[2]]
  
  # Address wildfire emissions and mass loss. 
  ##############################################################################################################
  ##############################################################################################################
  # CONFIRM THAT DUFF COMBUSTION RATE IS THE SAME AS THE FOLIAGE COMBUSTION RATE
  ##############################################################################################################
  ############################################################################################################## 
  wildfire_output <- annual_wildfire_fun(study_area_FCID,residue.segment = "Scattered",year.i)
  wildfire_emissions <- wildfire_output[[1]]
  study_area_FCID <- wildfire_output[[2]]
  
  wildfire_output <- annual_wildfire_fun(study_area_FCID,residue.segment = "Piled",year.i)
  wildfire_emissions <- wildfire_emissions + wildfire_output[[1]]
  study_area_FCID <- wildfire_output[[2]]
  
  wildfire_output <- annual_wildfire_fun(study_area_FCID,residue.segment = "Recovered",year.i)
  wildfire_emissions <- wildfire_emissions + wildfire_output[[1]]
  study_area_FCID <- wildfire_output[[2]]
  
  wildfire_output <- duff_annual_wildfire_fun(study_area_FCID,year.i)
  wildfire_emissions <- wildfire_emissions + wildfire_output[[1]]
  study_area_FCID <- wildfire_output[[2]]
  
  # Add decay and wildfire to the century emissions profile
  century_emissions_profile[1,':='(CO2_tonnes = CO2_tonnes + decay_emissions[,CO2_tonnes] + wildfire_emissions[,CO2_tonnes],
                                   CO_tonnes = CO_tonnes + decay_emissions[,CO_tonnes] + wildfire_emissions[,CO_tonnes],
                                   N2O_tonnes = N2O_tonnes + decay_emissions[,N2O_tonnes] + wildfire_emissions[,N2O_tonnes],
                                   CH4_tonnes = CH4_tonnes + decay_emissions[,CH4_tonnes] + wildfire_emissions[,CH4_tonnes],
                                   NOx_tonnes = NOx_tonnes + decay_emissions[,NOx_tonnes] + wildfire_emissions[,NOx_tonnes],
                                   PMUnder10um_tonnes = PMUnder10um_tonnes + decay_emissions[,PMUnder10um_tonnes] + wildfire_emissions[,PMUnder10um_tonnes],
                                   PMUnder2.5um_tonnes = PMUnder2.5um_tonnes + decay_emissions[,PMUnder2.5um_tonnes] + wildfire_emissions[,PMUnder2.5um_tonnes],
                                   SOx_tonnes = SOx_tonnes + decay_emissions[,SOx_tonnes] + wildfire_emissions[,SOx_tonnes],
                                   VOC_tonnes = VOC_tonnes + decay_emissions[,VOC_tonnes] + wildfire_emissions[,VOC_tonnes],
                                   char_tonnes = char_tonnes + decay_emissions[,char_tonnes] + wildfire_emissions[,char_tonnes]
                           )]
}

# In addition to the 100 year emission profiles, we need:
# 1) The total available residue base (Piled_INITIAL + Scattered_INITIAL + Recovered_INITIAL)
total_residue_base <- study_area_FCID[,sum(Recovered_CWD_tonsAcre_INITIAL, Recovered_FWD_tonsAcre_INITIAL, Recovered_Foliage_tonsAcre_INITIAL, Piled_CWD_tonsAcre_INITIAL, Piled_FWD_tonsAcre_INITIAL, Piled_Foliage_tonsAcre_INITIAL, Scattered_CWD_tonsAcre_INITIAL, Scattered_FWD_tonsAcre_INITIAL, Scattered_Foliage_tonsAcre_INITIAL)] * cell_to_acres

# 2) The total technically recovered residue (Recovered_INITIAL)
technically_recoverable_residue <- study_area_FCID[,sum(Recovered_CWD_tonsAcre_INITIAL, Recovered_FWD_tonsAcre_INITIAL, Recovered_Foliage_tonsAcre_INITIAL)] * cell_to_acres

# 3) The total mass sent to the power plant (mass_to_plant)
total_mass_to_power_plant <- study_area_FCID[,sum(mass_to_plant_tonsAcre)] * cell_to_acres

# 4) The total energy generated, in MWHe. This is power_plant_production

Sys.time()

```











