This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
#source("class_LocationData.R")
source("class_ModuleOutput.R")
source("harvest-processing.R")

```

Load needed library functions
```{r}
library(data.table)
library(raster)
library(rgdal)

```

To make multiple runs with different options, easier, we're putting all user options and filepaths in an external csv file,
which we read in here.
```{r}
user_input_filepath <- '/Volumes/744GB-Storage/Dropbox/serc/carbcat/cbrec_inputs.csv'
user_inputs <- data.table(read.csv(user_input_filepath, stringsAsFactors = FALSE))
```

Load up the location-specific information gleaned from GIS data. 
Originally, we planned on using a location.data object ("this.location") containing the following slots:

1) land.ownership = "character"
2) forestry.decay.rates = "data.frame"
3) slope = "numeric"
4) biomass.market.volume = "character"
5) pulp.market = "logical"
6) primary.harvest.species = "character"

However, based on experience from the webtool, the location.data object will likely be too cumbersome to 
use in offline analysis, and we handle the webtool with Python to avoid also having to coordinate with R.

We want to be able to analyze on the level of individal tiles, if necessary. A large data table will allow
us to do this more quickly and easily than a location data object, although a similar construction may make
sense for user-defined variables.

For reference: here's what we had planned for the location.data object If you want to make a fresh location 
object, use this code: (forestry decay currently set for Excel location FarNorCal)
this.location <- new("location.data",
                          land.ownership = "Private",
                          forestry.decay.rates = data.frame(scattered.CO2.k=-0.08,
                                                            scattered.CH4.k=-0.06,
                                                            scattered.N2O.k=-0.09,
                                                            piled.CO2.k=-0.04,
                                                            piled.CH4.k=-0.054,
                                                            piled.N2O.k=-0.081),
                          slope = 0,
                          biomass.market.volume = "High Volume",
                          pulp.market = FALSE,
                          primary.harvest.species = "Corn")

For forestry data:
To load up the location-specific date, first we load the FCID_WGS ratser layer.This has over a billion data points, and may
crash RStudio. In many cases, we will crop the dataset down to a shapefile supplied by the user (or, more accurately, mask the dataset).
If the dataset is full, most of those points are empty. In either case, once loaded, convert the RasterLayer to a data frame, and extract
the subset of points that correspond to actual data. 

Once we have the smaller data set, convert to a data table and combine with the residue and decay tables.

For agricultural data:
(TBA)
```{r}
if(user_inputs[variable=='ag_or_forest',value]=='forest') {
  full_CA_raster <- raster(user_inputs[variable=='fcid_wgs_filepath',value])
### Uncomment these lines back out when we have a slope file that matches the coordinate system of the FCID raster
  # slope_raster <- raster(user_inputs[variable=='slope_filepath',value])
  # names(slope_raster) <- "cell_slope"
  ### 
  
  # If the user inputs specify a study area mask file, load the shapefile and mask the raster to the shape file.
  if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
    study_area_mask <- readOGR(user_inputs[variable=='study_area_mask_file',value])
    full_CA_raster <- mask(full_CA_raster,study_area_mask)
### Uncomment these lines back out when we have a slope file in WGS
    # slope_raster <- mask(slope_raster,study_area_mask)
###    
  }
  
  # convert raster objects to data frames. This may crash things.
    ##########################################################################################
  ##########################################################################################
  # Look into if we can combine the subset line below into the as.data.frame line here. Also, 
  # look if we can stack FCID and slope rasters to see if we can load them at the same time.
  ##########################################################################################
    ##########################################################################################
  full_CA_df <- as.data.frame(full_CA_raster,xy=TRUE)

    # The full raster dataset is a square, so it will include non-forested areas within California, a chunk of the Pacifc Ocean,
  # and a fair bit of Nevada. These locations will have an FCID value of NA; trim it out using subset()
  full_CA_df <- subset(full_CA_df,!is.na(FCID_WGS))
  
  ### Uncomment these lines back out when we have a slope file that matches the coordinate system of the FCID raster 
  # Repeat with slope
  # slope_df <- as.data.frame(slope_raster,xy=TRUE)
  
  # The full raster dataset is a square, so it will include non-forested areas within California, a chunk of the Pacifc Ocean,
  # and a fair bit of Nevada. These locations will have an FCID value of NA; trim it out using subset()
  # slope_df <- subset(slope_df,!is.na(cell_slope))
  ###
  
  # Convert to a data table, and delete the data frame
  full_CA_FCID <- data.table(full_CA_df)
  full_CA_df <- NULL
  setkey(full_CA_FCID,x,y)
  
  ############
  # When we have a slope file projected in the same coordinate system of the FCID raster, we can remove this. and uncomment some of the other lines. Until then, let's
  # make a fake data set from full_CA_FCID. 
  slope_dt <- copy(full_CA_FCID)
  slope_dt[,cell_slope:=FCID_WGS/1e9]
  slope_dt[,FCID_WGS:=NULL]
  setkey(slope_dt,x,y)
  # REMEMBER TO DELETE THIS AFTER WE HAVE MATCHING SLOPE AND FCID RASTER
  ############
  
  ### Uncomment these lines back out when we have a slope file that matches the coordinate system of the FCID raster 
  # Repeat with slope
  # slope_dt <- data.table(slope_df)
  # slope_df <- NULL
  # setkey(slope_dt,x,y)
  ###
  
  # Combine the slope with the FCID data tables - THIS MAY NOT BE NECESSARY IF WE CAN LOAD AS STACKS.
  full_CA_FCID <- full_CA_FCID[slope_dt]
  # THERE MAY BE SOME ADJUSTMENTS NEEDED ONCE WE USE A REAL SLOPE RASTER
  
  # Delete the slope data table to save on memory
  slope_dt <- NULL
  
  # Read in the residue load values from a csv file. These values are indexed by FCID_WGS, so that is how we will join the 2 tables
  fcid_table <- data.table(read.csv(user_inputs[variable=='residue_treatment_filepath',value]))
  setkey(fcid_table,FCID2018)
  setkey(full_CA_FCID,FCID_WGS)
  full_CA_FCID <- full_CA_FCID[fcid_table[Treatment==user_inputs[variable=='treatment_type',value]]]
  setkey(full_CA_FCID,x,y)
  
  # There will be some overlap for FCID values that don't appear in the data set. They will have non-existant x & y values. Trim them.
  full_CA_FCID <- full_CA_FCID[!is.na(x)]
  
  # Eliminate the treatment and FCID columns, we do not need them.
  full_CA_FCID[,':='(FCID_WGS=NULL,Treatment=NULL)]
  
  # We have a full table of WGS coordinates and FCID values. Decay and fire values will be pre-run in tile format, so we will need to load
  # the tiles up into the main WGS table.
}

if(user_inputs[variable=='ag_or_forest',value]=='agricultural') {
  print('This code has yet to be written')
}

```

We now have a spatially-indexed data table with residue loading information and cell slope values. Now we figure out what the technically recoverable residue is.

# DEVELOPMENT UPDATE:
full_CA_FCID is too big to run in its entirety (issue of RAM). For development (and possibly for other runs), we need to break it into smaller data sets.
```{r}
# For development
full_CA_FCID <- full_CA_FCID[1:10000000,]
```

```{r}
# The harvest system and type will vary by slope; read in the harvest system file to get the slope criteria
harvest_system_criteria <- data.table(read.csv(user_inputs[variable=='harvest_system_file',value]))

# Remove the harvest systems screen out by having min/max slopes less than 0
harvest_system_criteria <- harvest_system_criteria[min_slope>=0&max_slope>=0,]

# If any of the slope criteria overlaps, we will run into a problem. I want to program a check for that here, but don't know how I want to do that. 
# Note that we will assume min criteria is inclusive (i.e. x >= min), max is exclusive (i.e. x < max). So, for complete criteria, the min should be 0, the max should be greater than 1. 
# The other mins/maxes should have a match in the data set.
# <Insert code for check here>

#######################################################################################################################################################
# Cell slope DOES NOT max out at 100%. Add an addtional category "Not_Harvestable", for cell slopes that prevent any kind of harvest.
#######################################################################################################################################################

# Apply the appropriate harvest system based on cell slope
full_CA_FCID[,harvest_system := harvest_system_criteria[min_slope==min(min_slope),harvest_system]]

for(row.i in nrow(harvest_system_criteria[min_slope!=min(min_slope)])) {
  full_CA_FCID[cell_slope >= harvest_system_criteria[row.i,min_slope] & cell_slope < harvest_system_criteria[row.i,max_slope],harvest_system := harvest_system_criteria[row.i,harvest_system]]
}

# The technically available residues will be based on silvicultural treatment, harvest system/type (currently the harvest_system column),
# burn type, biomass collection, and pulp market. Within a scenario, treatment, burn type, biomass collection, and pulp market are decided 
# across the entire study area. Harvest system will vary based on slope. Rather than create an ID for full_CA_FCID and merging with the complete scenario martix,
# create a smaller scenario matrix filtered through the user inputs, and merge with full_CA_FCID based upon harvest_system.
complete_scenario_matrix <- data.table(read.csv(user_inputs[variable=='scenario_matrix_file',value]))

# Trim to the treatment, burn type, biomass collection, and pulp market
scenario_matrix <- copy(complete_scenario_matrix[Silvicultural.Treatment==user_inputs[variable=='treatment_type',value] & Burn.Type==user_inputs[variable=='burn_type',value] & Biomass.Collection==user_inputs[variable=='biomass_collection',value] & Pulp.Market==user_inputs[variable=='has_pulp_market',value],])

# Running into a memory issue here; we're looking at 158 million rows and 12 columns, and merging with the scenario matrix would more than double that.
# We're going to try breaking up the scenario matrix into one segment at a time (recovered, merchantable, (do we need merchantable?), landing piled, field piled, scattered)
# Merge one segment of scenario matrix at a time, transform the needed columns, and then clear out. We're about at max data table memory.

########################################
# Combine stem and bark residues.
########################################

# Merge senario matrix with full_CA_FCID
scenario_matrix[,merge_column := paste(Harvest.System,Harvest.Type,sep='-')]
scenario_matrix[,':='(Silvicultural.Treatment=NULL, Harvest.System=NULL, Harvest.Type=NULL, Burn.Type=NULL, Biomass.Collection=NULL, Pulp.Market=NULL)]
setkey(scenario_matrix,merge_column)
setkey(full_CA_FCID,harvest_system)
full_CA_FCID <- scenario_matrix[full_CA_FCID]


########################################
# Old code - column names have changed
# Update 2/19: I'm not seeing this? 
########################################

# Combine the technically available fractions with the gross resource base.
full_CA_FCID[,':='(Recovered_Stem9Plus_tonsAcre = Recovered_Stem9Plus * Stem9Plus_tonsAcre,
                   Recovered_Stem6to9_tonsAcre = Recovered_Stem6to9 * Stem6to9_tonsAcre,
                   Recovered_Stem4to6_tonsAcre = Recovered_Stem4to6 * Stem4to6_tonsAcre,
                   Recovered_Bark9Plus_tonsAcre = Recovered_Bark9Plus * Bark9Plus_tonsAcre,
                   Recovered_Bark6to9_tonsAcre = Recovered_Bark6to9 * Bark6to9_tonsAcre,
                   Recovered_Bark4to6_tonsAcre = Recovered_Bark4to6 * Bark4to6_tonsAcre,
                   Recovered_Branch_tonsAcre = Recovered_Branch * Branch_tonsAcre,
                   Recovered_Foliage_tonsAcre = Recovered_Foliage * Foliage_tonsAcre,
                   Merchantable_Stem9Plus_tonsAcre = Merchantable_Stem9Plus * Stem9Plus_tonsAcre,
                   Merchantable_Stem6to9_tonsAcre = Merchantable_Stem6to9 * Stem6to9_tonsAcre,
                   Merchantable_Stem4to6_tonsAcre = Merchantable_Stem4to6 * Stem4to6_tonsAcre,
                   Merchantable_Bark9Plus_tonsAcre = Merchantable_Bark9Plus * Bark9Plus_tonsAcre,
                   Merchantable_Bark6to9_tonsAcre = Merchantable_Bark6to9 * Bark6to9_tonsAcre,
                   Merchantable_Bark4to6_tonsAcre = Merchantable_Bark4to6 * Bark4to6_tonsAcre,
                   Merchantable_Branch_tonsAcre = Merchantable_Branch * Branch_tonsAcre,
                   Merchantable_Foliage_tonsAcre = Merchantable_Foliage * Foliage_tonsAcre,
                   LandingPiled_Stem9Plus_tonsAcre = LandingPiled_Stem9Plus * Stem9Plus_tonsAcre,
                   LandingPiled_Stem6to9_tonsAcre = LandingPiled_Stem6to9 * Stem6to9_tonsAcre,
                   LandingPiled_Stem4to6_tonsAcre = LandingPiled_Stem4to6 * Stem4to6_tonsAcre,
                   LandingPiled_Bark9Plus_tonsAcre = LandingPiled_Bark9Plus * Bark9Plus_tonsAcre,
                   LandingPiled_Bark6to9_tonsAcre = LandingPiled_Bark6to9 * Bark6to9_tonsAcre,
                   LandingPiled_Bark4to6_tonsAcre = LandingPiled_Bark4to6 * Bark4to6_tonsAcre,
                   LandingPiled_Branch_tonsAcre = LandingPiled_Branch * Branch_tonsAcre,
                   LandingPiled_Foliage_tonsAcre = LandingPiled_Foliage * Foliage_tonsAcre,
                   FieldPiled_Stem9Plus_tonsAcre = FieldPiled_Stem9Plus * Stem9Plus_tonsAcre,
                   FieldPiled_Stem6to9_tonsAcre = FieldPiled_Stem6to9 * Stem6to9_tonsAcre,
                   FieldPiled_Stem4to6_tonsAcre = FieldPiled_Stem4to6 * Stem4to6_tonsAcre,
                   FieldPiled_Bark9Plus_tonsAcre = FieldPiled_Bark9Plus * Bark9Plus_tonsAcre,
                   FieldPiled_Bark6to9_tonsAcre = FieldPiled_Bark6to9 * Bark6to9_tonsAcre,
                   FieldPiled_Bark4to6_tonsAcre = FieldPiled_Bark4to6 * Bark4to6_tonsAcre,
                   FieldPiled_Branch_tonsAcre = FieldPiled_Branch * Branch_tonsAcre,
                   FieldPiled_Foliage_tonsAcre = FieldPiled_Foliage * Foliage_tonsAcre,
                   Scattered_Stem9Plus_tonsAcre = Scattered_Stem9Plus * Stem9Plus_tonsAcre,
                   Scattered_Stem6to9_tonsAcre = Scattered_Stem6to9 * Stem6to9_tonsAcre,
                   Scattered_Stem4to6_tonsAcre = Scattered_Stem4to6 * Stem4to6_tonsAcre,
                   Scattered_Bark9Plus_tonsAcre = Scattered_Bark9Plus * Bark9Plus_tonsAcre,
                   Scattered_Bark6to9_tonsAcre = Scattered_Bark6to9 * Bark6to9_tonsAcre,
                   Scattered_Bark4to6_tonsAcre = Scattered_Bark4to6 * Bark4to6_tonsAcre,
                   Scattered_Branch_tonsAcre = Scattered_Branch * Branch_tonsAcre,
                   Scattered_Foliage_tonsAcre = Scattered_Foliage * Foliage_tonsAcre
)]

# Trim out the columns we no longer need
full_CA_FCID[,':='(Recovered_Stem9Plus = NULL, Stem9Plus_tonsAcre = NULL, Recovered_Stem6to9 = NULL, Stem6to9_tonsAcre = NULL, Recovered_Stem4to6 = NULL,
                   Stem4to6_tonsAcre = NULL, Recovered_Bark9Plus = NULL, Bark9Plus_tonsAcre = NULL, Recovered_Bark6to9 = NULL, Bark6to9_tonsAcre = NULL,
                   Recovered_Bark4to6 = NULL, Bark4to6_tonsAcre = NULL, Recovered_Branch = NULL, Branch_tonsAcre = NULL, Recovered_Foliage = NULL,
                   Foliage_tonsAcre = NULL, Merchantable_Stem9Plus = NULL, Merchantable_Stem6to9 = NULL, Merchantable_Stem4to6 = NULL,  Merchantable_Bark9Plus = NULL,
                   Merchantable_Bark6to9 = NULL, Merchantable_Bark4to6 = NULL, Merchantable_Branch = NULL, Merchantable_Foliage = NULL, LandingPiled_Stem9Plus = NULL,
                   LandingPiled_Stem6to9 = NULL, LandingPiled_Stem4to6 = NULL, LandingPiled_Bark9Plus = NULL, LandingPiled_Bark6to9 = NULL, LandingPiled_Bark4to6 = NULL, 
                   LandingPiled_Branch = NULL, LandingPiled_Foliage = NULL, FieldPiled_Stem9Plus = NULL, FieldPiled_Stem6to9 = NULL, FieldPiled_Stem4to6 = NULL, 
                   FieldPiled_Bark9Plus = NULL, FieldPiled_Bark6to9 = NULL, FieldPiled_Bark4to6 = NULL, FieldPiled_Branch = NULL, FieldPiled_Foliage = NULL,
                   Scattered_Stem9Plus = NULL, Scattered_Stem6to9 = NULL, Scattered_Stem4to6 = NULL, Scattered_Bark9Plus = NULL, Scattered_Bark6to9 = NULL,
                   Scattered_Bark4to6 = NULL, Scattered_Branch = NULL, Scattered_Foliage = NULL
)]

# We now have a data table of the tons per acre for each cell within the study area. No we analyze the use case (collecting residues for power plants), and the reference case (residues are not collected for power plants).

```

Load the decay rate rasters
```{r}


```



Calculating the Reference Case Emissions
```{r}
# The user input variable "burn_type" will specify the nature of the reference case: a value of "Pile Burn," "Broadcast Burn," or "Jackpot Burn" will be intentionally burned and then follow decay/wildfire, "None" will just follow decay/wildfire.



```


The use cases are going to need a variable to identify the specific use case: collect from landing only, collect from landing and broadcast burn, and collect residues from landing and field.



(The order of module calls will change, right now they are ordered by when I coded them.)

Harvest-Processing
```{r}
harvest.processing.output <- harvest.processing(ag.or.forest, treatment.type, initial.moisture, harvest.collection.year.diff, comminution.opt, post.harvest.processing, scattered.fraction, piled.fraction)
```

In-Field Emissions; will almost certainly be different whether it is ag or forestry.
```{r}
if(ag.or.forest=='Agriculture') {
  print("In-field ag module here")
} else if (ag.or.forest=='Forestry') {
  print("In-field forestry module here")
} else {
  cat("ag.or.forest give neither ag, nor forestry")
}






```











