This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
#source("class_LocationData.R")
source("class_ModuleOutput.R")
# source("harvest-processing.R")
source("prescribed-burned-functions.R")
source("decay-functions.R")
source('wildfire-functions.R')
source("misc-functions.R")
```

Load needed library functions
```{r}
load.libraries(c("data.table","raster","rgdal","rgeos","beepr")) # beepr isfor testing

```

To make multiple runs with different options, easier, we're putting all user options and filepaths in an external csv file,
which we read in here.
```{r}
user_input_filepath <- '/Volumes/744GB-Storage/Dropbox/serc/carbcat/cbrec_inputs.csv'
user_inputs <- data.table(read.csv(user_input_filepath, stringsAsFactors = FALSE))
```

Load up the location-specific information gleaned from GIS data. 
Originally, we planned on using a location.data object ("this.location") containing the following slots:

1) land.ownership = "character"
2) forestry.decay.rates = "data.frame"
3) slope = "numeric"
4) biomass.market.volume = "character"
5) pulp.market = "logical"
6) primary.harvest.species = "character"

However, based on experience from the webtool, the location.data object will likely be too cumbersome to 
use in offline analysis, and we handle the webtool with Python to avoid also having to coordinate with R.

We want to be able to analyze on the level of individal tiles, if necessary. A large data table will allow
us to do this more quickly and easily than a location data object, although a similar construction may make
sense for user-defined variables.

For reference: here's what we had planned for the location.data object If you want to make a fresh location 
object, use this code: (forestry decay currently set for Excel location FarNorCal)
this.location <- new("location.data",
                          land.ownership = "Private",
                          forestry.decay.rates = data.frame(scattered.CO2.k=-0.08,
                                                            scattered.CH4.k=-0.06,
                                                            scattered.N2O.k=-0.09,
                                                            piled.CO2.k=-0.04,
                                                            piled.CH4.k=-0.054,
                                                            piled.N2O.k=-0.081),
                          slope = 0,
                          biomass.market.volume = "High Volume",
                          pulp.market = FALSE,
                          primary.harvest.species = "Corn")

For forestry data:
To load up the location-specific date, first we load the FCID_code ratser layer.This has over a billion data points, and may
crash RStudio. In many cases, we will crop the dataset down to a shapefile supplied by the user (or, more accurately, mask the dataset).
If the dataset is full, most of those points are empty. In either case, once loaded, convert the RasterLayer to a data frame, and extract
the subset of points that correspond to actual data. 

Once we have the smaller data set, convert to a data table and combine with the residue and decay tables.

For agricultural data:
(TBA)
```{r}
if(user_inputs[variable=='ag_or_forest',value]=='forest') {
  study_area_raster <- raster(user_inputs[variable=='fcid_code_filepath',value])
  slope_raster <- raster(user_inputs[variable=='slope_filepath',value])
  names(slope_raster) <- "cell_slope"

  # If the user inputs specify a study area mask file, load the shapefile, crop the original raster to the shapefile extents, and mask the raster to the shape file.
  if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
    study_area_mask <- readOGR(user_inputs[variable=='study_area_mask_file',value])
    study_area_raster <- crop(study_area_raster,extent(study_area_mask))
    study_area_raster <- mask(study_area_raster,study_area_mask)
    slope_raster <- crop(slope_raster,extent(study_area_mask))
    slope_raster <- mask(slope_raster,study_area_mask)
  }
  
  # convert raster objects to data frames. This may crash things.
    ##########################################################################################
  ##########################################################################################
  # Look into if we can combine the subset line below into the as.data.frame line here. Also, 
  # look if we can stack FCID and slope rasters to see if we can load them at the same time.
  ##########################################################################################
    ##########################################################################################
  study_area_df <- as.data.frame(study_area_raster,xy=TRUE)
  
  names(study_area_df) <- c('x','y','FCID_code')
  
  # The full raster dataset is a square, so it will include non-forested areas within California, a chunk of the Pacifc Ocean,
  # and a fair bit of Nevada. These locations will have an FCID value of NA; trim it out using subset()
  study_area_df <- subset(study_area_df,!is.na(FCID_code))
  
  # Repeat with slope
  slope_df <- as.data.frame(slope_raster,xy=TRUE)
  slope_df <- subset(slope_df,!is.na(cell_slope))
  
  # Convert to a data table, and delete the data frame
  study_area_FCID <- data.table(study_area_df)
  study_area_df <- NULL
  setkey(study_area_FCID,x,y)
  
  # Repeat with slope
  slope_dt <- data.table(slope_df)
  slope_df <- NULL
  setkey(slope_dt,x,y)

  # Combine the slope with the FCID data tables - THIS MAY NOT BE NECESSARY IF WE CAN LOAD AS STACKS.
  study_area_FCID <- slope_dt[study_area_FCID]

  # Delete the slope data table to save on memory
  slope_dt <- NULL
  
  # Read in the residue load values from a csv file. These values are indexed by FCID_code, so that is how we will join the 2 tables
  fcid_table <- data.table(read.csv(user_inputs[variable=='residue_treatment_filepath',value]))
  setkey(fcid_table,FCID2018)
  setkey(study_area_FCID,FCID_code)
  study_area_FCID <- study_area_FCID[fcid_table[Treatment==user_inputs[variable=='treatment_type',value]]]
  setkey(study_area_FCID,x,y)
  
  # There will be some overlap for FCID values that don't appear in the data set. They will have non-existant x & y values. Trim them.
  study_area_FCID <- study_area_FCID[!is.na(x)]
  
  # Round the x and y values to the first decimal, otherwise rounding errors are going to muck with joins with the decay rates.
  study_area_FCID[,':='(x=round(x,digits=1),y=round(y,digits=1))]
  
  # Eliminate the treatment and FCID columns, we do not need them.
  study_area_FCID[,':='(FCID_code=NULL,Treatment=NULL)]
  
  # We have a full table of WGS coordinates and FCID values. 
  
  # Fire values will be pre-run in tile format, so we will need to load the tiles up into the main WGS table.
}

if(user_inputs[variable=='ag_or_forest',value]=='agricultural') {
  print('This code has yet to be written')
}

beep(6)
```

We now have a spatially-indexed data table with residue loading information and cell slope values. Now we figure out what the technically recoverable residue is.

```{r}
# The harvest system and type will vary by slope; read in the harvest system file to get the slope criteria
harvest_system_criteria <- data.table(read.csv(user_inputs[variable=='harvest_system_file',value]))

# Remove the harvest systems screen out by having min/max slopes less than 0
harvest_system_criteria <- harvest_system_criteria[min_slope>=0&max_slope>=0,]

# If any of the slope criteria overlaps, we will run into a problem. I want to program a check for that here, but don't know how I want to do that. 
# Note that we will assume min criteria is inclusive (i.e. x >= min), max is exclusive (i.e. x < max). So, for complete criteria, the min should be 0, the max should be greater than 1. 
# The other mins/maxes should have a match in the data set.
# <Insert code for check here>

#######################################################################################################################################################
# Cell slope DOES NOT max out at 100%. Add an addtional category "Not_Harvestable", for cell slopes that prevent any kind of harvest.
#######################################################################################################################################################

# Apply the appropriate harvest system based on cell slope
study_area_FCID[,harvest_system := harvest_system_criteria[1,harvest_system]]

for(row.i in 2:nrow(harvest_system_criteria)) {
  study_area_FCID[cell_slope >= harvest_system_criteria[row.i,min_slope] & cell_slope < harvest_system_criteria[row.i,max_slope],harvest_system := harvest_system_criteria[row.i,harvest_system]]
}

# The technically available residues will be based on silvicultural treatment, harvest system/type (currently the harvest_system column),
# burn type, biomass collection, and pulp market. Within a scenario, treatment, burn type, biomass collection, and pulp market are decided 
# across the entire study area. Harvest system will vary based on slope. Rather than create an ID for study_area_FCID and merging with the complete scenario martix,
# create a smaller scenario matrix filtered through the user inputs, and merge with study_area_FCID based upon harvest_system.
complete_scenario_matrix <- data.table(read.csv(user_inputs[variable=='scenario_matrix_file',value]))

# Trim to the treatment, burn type, biomass collection, and pulp market
scenario_matrix <- copy(complete_scenario_matrix[Silvicultural.Treatment==user_inputs[variable=='treatment_type',value] & Burn.Type==user_inputs[variable=='burn_type',value] & Biomass.Collection==user_inputs[variable=='biomass_collection',value] & Pulp.Market==user_inputs[variable=='has_pulp_market',value],])

# Running into a memory issue here; we're looking at 158 million rows and 12 columns, and merging with the scenario matrix would more than double that.
# We're going to try breaking up the scenario matrix into one segment at a time (recovered, merchantable, (do we need merchantable?), landing piled, field piled, scattered)
# Merge one segment of scenario matrix at a time, transform the needed columns, and then clear out. We're about at max data table memory.

########################################
# Combine stem and bark residues.
########################################

# Merge senario matrix with study_area_FCID
scenario_matrix[,merge_column := paste(Harvest.System,Harvest.Type,sep='-')]
scenario_matrix[,':='(Silvicultural.Treatment=NULL, Harvest.System=NULL, Harvest.Type=NULL, Burn.Type=NULL, Biomass.Collection=NULL, Pulp.Market=NULL)]
setkey(scenario_matrix,merge_column)
setkey(study_area_FCID,harvest_system)
study_area_FCID <- scenario_matrix[study_area_FCID]


########################################
# Old code - column names have changed
# Update 2/19: I'm not seeing this? 
########################################

# Combine the technically available fractions with the gross resource base.
study_area_FCID[,':='(Recovered_Stem9Plus_tonsAcre = Recovered_Stem9Plus * Stem9Plus_tonsAcre,
                   Recovered_Stem6to9_tonsAcre = Recovered_Stem6to9 * Stem6to9_tonsAcre,
                   Recovered_Stem4to6_tonsAcre = Recovered_Stem4to6 * Stem4to6_tonsAcre,
                   Recovered_Bark9Plus_tonsAcre = Recovered_Bark9Plus * Bark9Plus_tonsAcre,
                   Recovered_Bark6to9_tonsAcre = Recovered_Bark6to9 * Bark6to9_tonsAcre,
                   Recovered_Bark4to6_tonsAcre = Recovered_Bark4to6 * Bark4to6_tonsAcre,
                   Recovered_Branch_tonsAcre = Recovered_Branch * Branch_tonsAcre,
                   Recovered_Foliage_tonsAcre = Recovered_Foliage * Foliage_tonsAcre,
                   Merchantable_Stem9Plus_tonsAcre = Merchantable_Stem9Plus * Stem9Plus_tonsAcre,
                   Merchantable_Stem6to9_tonsAcre = Merchantable_Stem6to9 * Stem6to9_tonsAcre,
                   Merchantable_Stem4to6_tonsAcre = Merchantable_Stem4to6 * Stem4to6_tonsAcre,
                   Merchantable_Bark9Plus_tonsAcre = Merchantable_Bark9Plus * Bark9Plus_tonsAcre,
                   Merchantable_Bark6to9_tonsAcre = Merchantable_Bark6to9 * Bark6to9_tonsAcre,
                   Merchantable_Bark4to6_tonsAcre = Merchantable_Bark4to6 * Bark4to6_tonsAcre,
                   Merchantable_Branch_tonsAcre = Merchantable_Branch * Branch_tonsAcre,
                   Merchantable_Foliage_tonsAcre = Merchantable_Foliage * Foliage_tonsAcre,
                   LandingPiled_Stem9Plus_tonsAcre = LandingPiled_Stem9Plus * Stem9Plus_tonsAcre,
                   LandingPiled_Stem6to9_tonsAcre = LandingPiled_Stem6to9 * Stem6to9_tonsAcre,
                   LandingPiled_Stem4to6_tonsAcre = LandingPiled_Stem4to6 * Stem4to6_tonsAcre,
                   LandingPiled_Bark9Plus_tonsAcre = LandingPiled_Bark9Plus * Bark9Plus_tonsAcre,
                   LandingPiled_Bark6to9_tonsAcre = LandingPiled_Bark6to9 * Bark6to9_tonsAcre,
                   LandingPiled_Bark4to6_tonsAcre = LandingPiled_Bark4to6 * Bark4to6_tonsAcre,
                   LandingPiled_Branch_tonsAcre = LandingPiled_Branch * Branch_tonsAcre,
                   LandingPiled_Foliage_tonsAcre = LandingPiled_Foliage * Foliage_tonsAcre,
                   FieldPiled_Stem9Plus_tonsAcre = FieldPiled_Stem9Plus * Stem9Plus_tonsAcre,
                   FieldPiled_Stem6to9_tonsAcre = FieldPiled_Stem6to9 * Stem6to9_tonsAcre,
                   FieldPiled_Stem4to6_tonsAcre = FieldPiled_Stem4to6 * Stem4to6_tonsAcre,
                   FieldPiled_Bark9Plus_tonsAcre = FieldPiled_Bark9Plus * Bark9Plus_tonsAcre,
                   FieldPiled_Bark6to9_tonsAcre = FieldPiled_Bark6to9 * Bark6to9_tonsAcre,
                   FieldPiled_Bark4to6_tonsAcre = FieldPiled_Bark4to6 * Bark4to6_tonsAcre,
                   FieldPiled_Branch_tonsAcre = FieldPiled_Branch * Branch_tonsAcre,
                   FieldPiled_Foliage_tonsAcre = FieldPiled_Foliage * Foliage_tonsAcre,
                   Scattered_Stem9Plus_tonsAcre = Scattered_Stem9Plus * Stem9Plus_tonsAcre,
                   Scattered_Stem6to9_tonsAcre = Scattered_Stem6to9 * Stem6to9_tonsAcre,
                   Scattered_Stem4to6_tonsAcre = Scattered_Stem4to6 * Stem4to6_tonsAcre,
                   Scattered_Bark9Plus_tonsAcre = Scattered_Bark9Plus * Bark9Plus_tonsAcre,
                   Scattered_Bark6to9_tonsAcre = Scattered_Bark6to9 * Bark6to9_tonsAcre,
                   Scattered_Bark4to6_tonsAcre = Scattered_Bark4to6 * Bark4to6_tonsAcre,
                   Scattered_Branch_tonsAcre = Scattered_Branch * Branch_tonsAcre,
                   Scattered_Foliage_tonsAcre = Scattered_Foliage * Foliage_tonsAcre
)]

# Trim out the columns we no longer need
study_area_FCID[,':='(Recovered_Stem9Plus = NULL, Stem9Plus_tonsAcre = NULL, Recovered_Stem6to9 = NULL, Stem6to9_tonsAcre = NULL, Recovered_Stem4to6 = NULL,
                   Stem4to6_tonsAcre = NULL, Recovered_Bark9Plus = NULL, Bark9Plus_tonsAcre = NULL, Recovered_Bark6to9 = NULL, Bark6to9_tonsAcre = NULL,
                   Recovered_Bark4to6 = NULL, Bark4to6_tonsAcre = NULL, Recovered_Branch = NULL, Branch_tonsAcre = NULL, Recovered_Foliage = NULL,
                   Foliage_tonsAcre = NULL, Merchantable_Stem9Plus = NULL, Merchantable_Stem6to9 = NULL, Merchantable_Stem4to6 = NULL,  Merchantable_Bark9Plus = NULL,
                   Merchantable_Bark6to9 = NULL, Merchantable_Bark4to6 = NULL, Merchantable_Branch = NULL, Merchantable_Foliage = NULL, LandingPiled_Stem9Plus = NULL,
                   LandingPiled_Stem6to9 = NULL, LandingPiled_Stem4to6 = NULL, LandingPiled_Bark9Plus = NULL, LandingPiled_Bark6to9 = NULL, LandingPiled_Bark4to6 = NULL, 
                   LandingPiled_Branch = NULL, LandingPiled_Foliage = NULL, FieldPiled_Stem9Plus = NULL, FieldPiled_Stem6to9 = NULL, FieldPiled_Stem4to6 = NULL, 
                   FieldPiled_Bark9Plus = NULL, FieldPiled_Bark6to9 = NULL, FieldPiled_Bark4to6 = NULL, FieldPiled_Branch = NULL, FieldPiled_Foliage = NULL,
                   Scattered_Stem9Plus = NULL, Scattered_Stem6to9 = NULL, Scattered_Stem4to6 = NULL, Scattered_Bark9Plus = NULL, Scattered_Bark6to9 = NULL,
                   Scattered_Bark4to6 = NULL, Scattered_Branch = NULL, Scattered_Foliage = NULL
)]

# We now have a data table of the tons per acre for each cell within the study area. No we analyze the use case (collecting residues for power plants), and the reference case (residues are not collected for power plants).

```

Load the decay rate rasters
```{r}
# There are currently 3 decay rasters: one for CWD, FWD, and foliage. From our notes, there should be six rates (for piled and scattered), not just 3.
# Figure out if this is an issue.
CWD_decay_raster <- raster(user_inputs[variable=='CWD_decay_filepath',value])
FWD_decay_raster <- raster(user_inputs[variable=='FWD_decay_filepath',value])
foliage_decay_raster <- raster(user_inputs[variable=='foliage_decay_filepath',value])

# If the user inputs specify a study area mask file, we will have a shapefile loaded from earlier. Use the same shape file to crop and mask our rasters.
if(!is.na(user_inputs[variable=='study_area_mask_file',value])) {
  # CWD raster
  CWD_decay_raster <- crop(CWD_decay_raster,extent(study_area_mask))
  CWD_decay_raster <- mask(CWD_decay_raster,study_area_mask)
  
  # FWD raster  
  FWD_decay_raster <- crop(FWD_decay_raster,extent(study_area_mask))
  FWD_decay_raster <- mask(FWD_decay_raster,study_area_mask)
  
  # foliage raster
  foliage_decay_raster <- crop(foliage_decay_raster,extent(study_area_mask))
  foliage_decay_raster <- mask(foliage_decay_raster,study_area_mask)
}

# Now that the decay rasters are loaded and masked, convert them to data frames and then data tables
CWD_decay_df <- as.data.frame(CWD_decay_raster,xy=TRUE)
CWD_decay_rates <- data.table(CWD_decay_df)
CWD_decay_df <- NULL
setkey(CWD_decay_rates,x,y)
CWD_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

FWD_decay_df <- as.data.frame(FWD_decay_raster,xy=TRUE)
FWD_decay_rates <- data.table(FWD_decay_df)
FWD_decay_df <- NULL
setkey(FWD_decay_rates,x,y)
FWD_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

foliage_decay_df <- as.data.frame(foliage_decay_raster,xy=TRUE)
foliage_decay_rates <- data.table(foliage_decay_df)
foliage_decay_df <- NULL
setkey(foliage_decay_rates,x,y)
foliage_decay_rates[,':='(x=round(x,digits=1),y=round(y,digits=1))]

# Join decay data tables with the study area FCID, and then clear the data tables
setkey(study_area_FCID,x,y)
setkey(CWD_decay_rates,x,y)
setkey(FWD_decay_rates,x,y)
setkey(foliage_decay_rates,x,y)

study_area_FCID <- CWD_decay_rates[FWD_decay_rates[foliage_decay_rates[study_area_FCID]]]

# There may be a couple more NA points, with no reource available and no decay rate assigned. Clear it out.
study_area_FCID <- study_area_FCID[!is.na(CWD_cm)&!is.na(FWD_cm)&!is.na(Foliage_cm),]

CWD_decay_rates <- NULL
FWD_decay_rates <- NULL
foliage_decay_rates <- NULL

# Last step: for decay, we will actually need 6 decay rates: the 3 for scattered decay (CWD, FWD, foliage), and decay rates for the same material classes
# in piles. The piled rates are just the other rates multiplied by a scalar factor; this we can hard code:
piled_K_coeff <- 0.7516606 # 0.721265744184168; changed March 2019 to reflect proportion of ground contact within pile.

beep(4)
```
Add wildfire data and emissions factors. These are stored in .rds files by tile; there are over 13,000 tiles. We need to load the tile data that overlaps with
our study area, then the data needs to be cropped to match our study area exactly.

*NOTE* The fill wildfire data has not been processed yet, so to test out this operation, I am probably going to need to make some dummy data.

```{r}
# Load up the full tile shape file
full_tile_set <- readOGR(user_inputs[variable=="tile_shape_file",value])
study_area_tiles <- intersect(study_area_mask,full_tile_set)

# To get the tile IDs, convert study_area_tiles into a data frame and extract the ID column
tile_list <- as.data.frame(study_area_tiles)$ID

wildfire_data <- data.table()

# Cycle through tile_list, load the .rds files, and combine into a single data table.
for (tile in tile_list) {
  new_tile <- readRDS(paste(user_inputs[variable=="wildfire_data_directory",value],tile,".rds",sep=""))
  tile_data <- data.table(as.data.frame(new_tile,xy=TRUE))
  setkey(tile_data,x,y)
  wildfire_data <- rbind(wildfire_data,tile_data)
  tile_data <- NULL
}

# Round the x and y values to the first decimal, otherwise rounding errors are going to muck with joins.
wildfire_data[,':='(x=round(x,digits=1),y=round(y,digits=1))]
setkey(wildfire_data,x,y)

##############################################################################################################
##############################################################################################################
# BECAUSE WE ARE USING DUMMY DATA, WE NEED TO RENAME AND CREATE SOME MORE REALISTIC DUMMY DATA.
##############################################################################################################
##############################################################################################################
setnames(wildfire_data,"UW_FCID_no_wild","MassExposedToWildfire")
wildfire_data[,':='(MassExposedToWildfire = MassExposedToWildfire / 1e10,
                    CWD_CombustionFrac = runif(nrow(wildfire_data)),
                    FWD_CombustionFrac = runif(nrow(wildfire_data)),
                    Foliage_CombustionFrac = runif(nrow(wildfire_data))
                    )]

wildfire_data[,':='(CWD_CharFrac = (2/3) * (1 - CWD_CombustionFrac),
                    FWD_CharFrac = (2/3) * (1 - FWD_CombustionFrac),
                    Foliage_CharFrac = (2/3) * (1 - Foliage_CombustionFrac)
                    )]

wildfire_data[,':='(CWD_UnburendFrac = 1 - CWD_CombustionFrac - CWD_CharFrac,
                    FWD_UnburendFrac = 1 - FWD_CombustionFrac - FWD_CharFrac,
                    Foliage_UnburendFrac = 1 - Foliage_CombustionFrac - Foliage_CharFrac
                    )]

# Merge the wildfire data with study_area_FCID
study_area_FCID <- wildfire_data[study_area_FCID]
```


Calculating the Prescribed Burn/Decay/Wildfire Emissions
```{r}
##########################################################################################################################################################
# PRESCRIBED BURN HAPPENS BEFORE DECAY.
# MASS IS REMOVED FROM PILED CATEGORIES DIRECTLY, exposed but unburned mass remains in the original column for exposure to wildfire/decay 
##########################################################################################################################################################

# The user input variable "burn_type" will specify the nature of the scenario: a value of "Pile Burn," "Broadcast Burn," or "Jackpot Burn" will be intentionally burned and then follow decay/wildfire, "None" will just follow decay/wildfire.

# We will need to build out the code to perform a burn if we need to first, but for now let's build out the decay equations. I feel that will be the hard part.

# Step 1: combine all mass categories into CWD, FWD, and foliage. There will also be a duff column, though this will start empty. 
# There will be several categories with different decay rates - recovered, scattered (including merchantable breakage), field piled, and landing piled
study_area_FCID[,':='(Recovered_CWD_tonsAcre = Recovered_Stem9Plus_tonsAcre + Recovered_Stem6to9_tonsAcre + Recovered_Stem4to6_tonsAcre + Recovered_Bark9Plus_tonsAcre + Recovered_Bark6to9_tonsAcre + Recovered_Bark4to6_tonsAcre,
                      Scattered_CWD_tonsAcre = Merchantable_Stem9Plus_tonsAcre + Merchantable_Stem6to9_tonsAcre + Merchantable_Stem4to6_tonsAcre + Merchantable_Bark9Plus_tonsAcre + Merchantable_Bark6to9_tonsAcre + Merchantable_Bark4to6_tonsAcre + Scattered_Stem9Plus_tonsAcre + Scattered_Stem6to9_tonsAcre + Scattered_Stem4to6_tonsAcre + Scattered_Bark9Plus_tonsAcre + Scattered_Bark6to9_tonsAcre + Scattered_Bark4to6_tonsAcre,
                      LandingPiled_CWD_tonsAcre = 
LandingPiled_Stem9Plus_tonsAcre + LandingPiled_Stem6to9_tonsAcre + LandingPiled_Stem4to6_tonsAcre + LandingPiled_Bark9Plus_tonsAcre + LandingPiled_Bark6to9_tonsAcre + LandingPiled_Bark4to6_tonsAcre,
                      FieldPiled_CWD_tonsAcre = FieldPiled_Stem9Plus_tonsAcre + FieldPiled_Stem6to9_tonsAcre + FieldPiled_Stem4to6_tonsAcre + FieldPiled_Bark9Plus_tonsAcre + FieldPiled_Bark6to9_tonsAcre + FieldPiled_Bark4to6_tonsAcre + FieldPiled_Branch_tonsAcre + FieldPiled_Foliage_tonsAcre
)]

# Clear out old columns, as well as merchantable branch/foliage (which should've been empty anyway)
study_area_FCID[,':='(Recovered_Stem9Plus_tonsAcre = NULL, Recovered_Stem6to9_tonsAcre = NULL, Recovered_Stem4to6_tonsAcre = NULL, Recovered_Bark9Plus_tonsAcre = NULL, Recovered_Bark6to9_tonsAcre = NULL, 
                      Recovered_Bark4to6_tonsAcre = NULL, Merchantable_Stem9Plus_tonsAcre = NULL, Merchantable_Stem6to9_tonsAcre = NULL, Merchantable_Stem4to6_tonsAcre = NULL, Merchantable_Bark9Plus_tonsAcre = NULL,
                      Merchantable_Bark6to9_tonsAcre = NULL, Merchantable_Bark4to6_tonsAcre = NULL, Merchantable_Branch_tonsAcre=NULL, Merchantable_Foliage_tonsAcre = NULL, Scattered_Stem9Plus_tonsAcre = NULL,
                      Scattered_Stem6to9_tonsAcre = NULL, Scattered_Stem4to6_tonsAcre = NULL, Scattered_Bark9Plus_tonsAcre = NULL, Scattered_Bark6to9_tonsAcre = NULL, Scattered_Bark4to6_tonsAcre = NULL,
                      LandingPiled_Stem9Plus_tonsAcre = NULL, LandingPiled_Stem6to9_tonsAcre = NULL, LandingPiled_Stem4to6_tonsAcre = NULL, LandingPiled_Bark9Plus_tonsAcre = NULL, LandingPiled_Bark6to9_tonsAcre = NULL,
                      LandingPiled_Bark4to6_tonsAcre = NULL, FieldPiled_Stem9Plus_tonsAcre = NULL,FieldPiled_Stem6to9_tonsAcre = NULL, FieldPiled_Stem4to6_tonsAcre = NULL, FieldPiled_Bark9Plus_tonsAcre = NULL,
                      FieldPiled_Bark6to9_tonsAcre = NULL, FieldPiled_Bark4to6_tonsAcre = NULL
)]

# FWD consists of branches, and foliage is obviously foliage. Just rename the columns.
setnames(study_area_FCID,
         c("Recovered_Branch_tonsAcre","LandingPiled_Branch_tonsAcre","FieldPiled_Branch_tonsAcre","Scattered_Branch_tonsAcre"),
         c("Recovered_FWD_tonsAcre","LandingPiled_FWD_tonsAcre","FieldPiled_FWD_tonsAcre","Scattered_FWD_tonsAcre"))

# Copy the residue columns for LandingPiled, FieldPiled, and Scattered residues. These will be the initial mass residues in Year 1. We will also need some blank columns to track material exposed to fire but left unburned.
study_area_FCID[,':='(LandingPiled_CWD_tonsAcre_INITIAL = LandingPiled_CWD_tonsAcre,
                      LandingPiled_FWD_tonsAcre_INITIAL = LandingPiled_FWD_tonsAcre,
                      LandingPiled_Foliage_tonsAcre_INITIAL = LandingPiled_Foliage_tonsAcre,
                      FieldPiled_CWD_tonsAcre_INITIAL = FieldPiled_CWD_tonsAcre,
                      FieldPiled_FWD_tonsAcre_INITIAL = FieldPiled_FWD_tonsAcre,
                      FieldPiled_Foliage_tonsAcre_INITIAL = FieldPiled_Foliage_tonsAcre,
                      Scattered_CWD_tonsAcre_INITIAL = Scattered_CWD_tonsAcre,
                      Scattered_FWD_tonsAcre_INITIAL = Scattered_FWD_tonsAcre,
                      Scattered_Foliage_tonsAcre_INITIAL = Scattered_Foliage_tonsAcre
                      )]

# Make columns for duff, mass previously exposed to fire but unburnt, and year.i columns. If space becomes an issue, we can create/delete year.i column in the decay function, but I;m guessing that will hit our speed.
study_area_FCID[,':='(Duff_tonsAcre=0, decay_CWD_mass_year_i=0, decay_FWD_mass_year_i=0, decay_Foliage_mass_year_i=0,
                      fire_exposed_CWD_mass_year_i=0, fire_exposed_FWD_mass_year_i=0, fire_exposed_Foliage_mass_year_i=0, fire_exposed_Duff_mass_year_i=0,
                      prev_fired_CWD_mass=0, prev_fired_FWD_mass=0, prev_fired_Foliage_mass=0, prev_fired_Duff_mass=0)]

# and mass emissions and charred material for years 1:100
study_area_FCID[,paste("Emissions_year_",seq(1,100),sep=""):=0]
study_area_FCID[,paste("char_year_",seq(1,100),sep=""):=0]

# Cycle through 100 years of emissions. Each year, we need to:
# 1) Calculate the mass lost in year i
# 2) Use the mass lost to atmosphere/duff ratios to calculate the mass lost to duff and atmosphere
# 3) Update the dynamic residue mass
# 4) Apply decay to the duff column, add emissions to emissions columns, and update duff mass.

# Repeat for Scattered, LandingPiled, and FieldPiled
residue.segments <- c("Scattered","FieldPiled","LandingPiled")

# Wildfire emissions will be calculated here alongside decay. We need to change how we track foliage - to - duff conversions; rather than existing mass vs initial (which would include fire loss), track when decay would bring us below the 50% threshold. NOTE TO ANDY: if you get the brilliant idea to track decay loss, this will not work - if (theoretically) 75% of the mass is lost to wildfire before it can decay, the transition to duff would never happen. Base the switch on the expected decay.
# Also, apply all decay (including duff) before wildfire emissions.

# Output should be a 100 row-X xolumn data table of combined emissions for study area by emissions type (i.e. decay, wildfire, other use....). See output template for more info.

for (residue.segment in residue.segments) {
  print(residue.segment)
  for (year.i in 1:100) {
    print(year.i)
    
    # Calculate emissions and mass lost from prescribed burning. This will only happen in year 1, and if the burn_type variable gives a prescribed burn.
    if(year.i==1 & user_inputs[variable=='burn_type',value] != "None") {
      # Make sure that the residue segment matches correctly with the prescribed burn method
      if(residue.segment == "Scattered" & user_inputs[variable=='burn_type',value] == "Broadcast Burn") {
         study_area_FCID <- prescribed_burn_fun(study_area_FCID, residue.segment, user_inputs[variable=='burn_type',value])
      }
      if(residue.segment == "FieldPiled" & user_inputs[variable=='burn_type',value] == "Jackpot Burn") {
         study_area_FCID <- prescribed_burn_fun(study_area_FCID, residue.segment, user_inputs[variable=='burn_type',value])
      }
      if(residue.segment == "LandingPiled" & user_inputs[variable=='burn_type',value] == "Pile Burn") {
         study_area_FCID <- prescribed_burn_fun(study_area_FCID, residue.segment, user_inputs[variable=='burn_type',value])
      }
    }
    
    # Calculate the total decayed mass
    study_area_FCID <- decay_fun(study_area_FCID,residue.segment,year.i)
    
    # Address wildfire emissions and mass loss. 
    ##############################################################################################################
    ##############################################################################################################
    # CONFIRM THAT DUFF COMBUSTION RATE IS THE SAME AS THE FOLIAGE COMBUSTION RATE
    ##############################################################################################################
    ############################################################################################################## 
    study_area_FCID <- annual_wildfire_fun(study_area_FCID,residue.segment,year.i)
    
  }
  # I think we need to re-set the duff for the new residue segment so duff does not get double-counted.
  study_area_FCID[,':='(Duff_tonsAcre = 0, prev_fired_Duff_mass = 0)]
}

```

Calculating harvest, processing, and use emissions.


(The order of module calls will change, right now they are ordered by when I coded them.)

Harvest-Processing
```{r}
# harvest.processing.output <- harvest.processing(ag.or.forest, treatment.type, initial.moisture, harvest.collection.year.diff, comminution.opt, post.harvest.processing, scattered.fraction, piled.fraction)
```

In-Field Emissions; will almost certainly be different whether it is ag or forestry.
```{r}
# if(ag.or.forest=='Agriculture') {
#   print("In-field ag module here")
# } else if (ag.or.forest=='Forestry') {
#   print("In-field forestry module here")
# } else {
#   cat("ag.or.forest give neither ag, nor forestry")
# }
```











