This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
source("class_LocationData.R")
source("class_ModuleOutput.R")
source("harvest-processing.R")



```

Load up the location-specific information gleaned from GIS data. 
We don't yet know how we are going to interface GIS data with R, but we do know that information
will be stored in a location.data object. Currently, a location.data object contains the following slots:

1) land.ownership = "character"
2) size.class.decay.rates = "data.frame"
3) slope = "numeric"
4) biomass.market.volume = "character"
5) pulp.market = "logical"
6) primary.harvest.species = "character"

For now, load up a location.data object with dummy data. If you want to make a fresh location 
object, use this code: (forestry decay currently set for Excel location FarNorCal)
dummy.location.obj <- new("location.data",
                          land.ownership = "Private",
                          forestry.decay.rates = data.frame(scattered.CO2.k=-0.08,
                                                            scattered.CH4.k=-0.06,
                                                            scattered.N2O.k=-0.09,
                                                            piled.CO2.k=-0.04,
                                                            piled.CH4.k=-0.054,
                                                            piled.N2O.k=-0.081),
                          slope = 0,
                          biomass.market.volume = "High Volume",
                          pulp.market = FALSE,
                          primary.harvest.species = "Corn")
```{r}
load("dummy-location-obj.Rdata")

```

We also need to load the other user-input data not expressly tied to location (things like "ag.o.forestry", or
the agricultural residue under consideration)

Again, I don't know how this will look in the final product, but for now, just define some dummy values.
```{r}



```