This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
source("class_LocationData.R")
source("class_ModuleOutput.R")
source("harvest-processing.R")



```

Load up the location-specific information gleaned from GIS data. 
We don't yet know how we are going to interface GIS data with R, but we do know that information
will be stored in a location.data object. Currently, a location.data object contains the following slots:

1) land.ownership = "character"
2) size.class.decay.rates = "data.frame"
3) slope = "numeric"
4) biomass.market.volume = "character"
5) pulp.market = "logical"
6) primary.harvest.species = "character"

For now, load up a location.data object with dummy data
```{r}
load("dummy-location-obj.Rdata")

```

We also need to load the other user-input data not expressly tied to location (things like "ag.o.forestry", or
the agricultural residue under consideration)

Again, I don't know how this will look in the final product, but for now, just define some dummy values.
```{r}



```