This script will contain the main code for CARBCAT, while calling on separate modules for
model segments.

Source relevant module and function files.
```{r}
source("class_LocationData.R")
source("class_ModuleOutput.R")
source("harvest-processing.R")



```

Load up the location-specific information gleaned from GIS data. 
We don't yet know how we are going to interface GIS data with R, but we do know that information
will be stored in a location.data object. Currently, a location.data object contains the following slots:

1) land.ownership = "character"
2) forestry.decay.rates = "data.frame"
3) slope = "numeric"
4) biomass.market.volume = "character"
5) pulp.market = "logical"
6) primary.harvest.species = "character"

Throughout this script, the variable for the location object will be named "this.location." It will be a global
variable, used throughout functions and modules.

For now, load up a location.data object with dummy data. If you want to make a fresh location 
object, use this code: (forestry decay currently set for Excel location FarNorCal)
this.location <- new("location.data",
                          land.ownership = "Private",
                          forestry.decay.rates = data.frame(scattered.CO2.k=-0.08,
                                                            scattered.CH4.k=-0.06,
                                                            scattered.N2O.k=-0.09,
                                                            piled.CO2.k=-0.04,
                                                            piled.CH4.k=-0.054,
                                                            piled.N2O.k=-0.081),
                          slope = 0,
                          biomass.market.volume = "High Volume",
                          pulp.market = FALSE,
                          primary.harvest.species = "Corn")
```{r}
#load("dummy-location-obj.Rdata")
this.location <- new("location.data",
                          land.ownership = "Private",
                          forestry.decay.rates = data.frame(scattered.CO2.k=-0.08,
                                                            scattered.CH4.k=-0.06,
                                                            scattered.N2O.k=-0.09,
                                                            piled.CO2.k=-0.04,
                                                            piled.CH4.k=-0.054,
                                                            piled.N2O.k=-0.081),
                          slope = 0,
                          biomass.market.volume = "High Volume",
                          pulp.market = FALSE,
                          forest.species = "Corn")

########################################################################################
# Forestry applications will have dominant and sub-dominant species, stored as a single
# variable (i.e. "BOOS" = "Blue Oak Dominant, Other Soft sub-dominant). We wil keep that 
# as a string variable in the location data object.
#
# Agricultural species will be entirely user-dependent, and thus will have a different
# variable name and will not be in location data.
########################################################################################


```
We also need to load the other user-input data not expressly tied to location (things like "ag.or.forestry", or
the agricultural residue under consideration). I imagine that this will be input from the Shiny user interface.

For now, just define some dummy values. If "burn.year" isn't applicable, set it arbitrarily high here.
```{r}
# Forestry option
# ag.or.forest <- 'Forestry'
# treatment.type <- 'None'
# initial.moisture <- 35
# harvest.collection.year.diff <- 4
# comminution.opt <- 'Grinding'
# post.harvest.processing <- 'None'
# scattered.fraction <- 0.5
# piled.fraction <- 0.5
# burn.or.decay <- "Pile Burn" # "Decay Only", "Pile Burn", "In-Field Burn"
# burn.year <- 1 # Year in which residues are burned - if no residue is being burned, this will be set arbitrarily large in-module.
# land.management <- "None" #"None", "Scattering", "Re-incorporation"

# Ag option - ADD SPECIES
ag.or.forest <- 'Agriculture'
treatment.type <- 'None'
initial.moisture <- 35
harvest.collection.year.diff <- 4
comminution.opt <- 'Grinding'
post.harvest.processing <- 'None'
scattered.fraction <- 0.5
piled.fraction <- 0.5
burn.or.decay <- "Pile Burn" # "Decay Only", "Pile Burn", "In-Field Burn"
burn.year <- 15 # Year in which residues are burned - if no residue is being burned, this will be set arbitrarily large in-module.
land.management <- "None" #"None", "Scattering", "Re-incorporation"

# If there is no burning, then set the burn year absurdly high.
if(burn.or.decay=="Decay Only") { burn.year <- 802701 }

```

(The order of module calls will change, right now they are ordered by when I coded them.)

Harvest-Processing
```{r}
harvest.processing.output <- harvest.processing(ag.or.forest, treatment.type, initial.moisture, harvest.collection.year.diff, comminution.opt, post.harvest.processing, scattered.fraction, piled.fraction)
```

In-Field Emissions; will almost certainly be different whether it is ag or forestry.
```{r}
if(ag.or.forest=='Agriculture') {
  print("In-field ag module here")
} else if (ag.or.forest=='Forestry') {
  print("In-field forestry module here")
} else {
  cat("ag.or.forest give neither ag, nor forestry")
}






```











